---
title: "Lab 11 - Grading the professor, Pt. 2"
author: "Ben Waggener"
date: "Insert date here"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

##Exercise 1

"Fit a linear model (one you have fit before): m_bty, predicting average professor evaluation score based on average beauty rating (bty_avg) only. Write the linear model, and note the  
R2 and the adjusted R2."

*score = 3.88 + .066(beauty average)
R2 = .035 adjusted = .033*   


```{r exercise1_code}
evals <- openintro::evals

m_bty <- lm(score ~ bty_avg, data = evals)
summary(m_bty)

```

## Exercise 2
"Fit a linear model (one you have fit before): m_bty_gen, predicting average professor evaluation score based on average beauty rating (bty_avg) and gender. Write the linear model, and note the  
R 2 and the adjusted R2."

*score = 3.75 + .074(average beauty score) + .17(gender_male)
R2 = .059, adjusted = .055*  



```{r exercise2_code}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
summary(m_bty_gen)


```

## Exercise 3


*for this linear model, the incept represents the evaluation score for a hypothetical person who received a 0 for their average beauty rating and is a woman. The slope for bty_avg means that increasing a beauty average score by 1 results in a greater evaluation score by .074--on average. The slope for gender means that being male, compared to female, increases the evaluation score by .17--on average*

## Exercise 4

almost 6% of the variability is explained by this model accounting for average beauty and gender.

##Exercise 5

score = 3.92 + .074(average beauty score)--- model for men

## Exercise 6
If two people have the same beauty rating, on average, the male professor would get higher evaluation scores if the other person is female.

##Exercise 7
/"How does the relationship between beauty and evaluation score vary between male and female professors?"

for female professors, a one point increase in beauty scores only increase their overall evaluation by .031 while for men it increases by .080. So beauty has a stronger influence on men compared to female's evaluation scores.

```{r interaction}
int_m_bty_gen <- lm(score ~ bty_avg * gender, data = evals)
summary(int_m_bty_gen)
```

##Exercise 8
the model with gender accounts for more variability in the scores meaning that gender and beauty explains more than just beauty alone. Gender adds additional predictive power even if beauty is already being conseridered.

##Exercise 9
Yes adding gender changed the slope of beauty in the model.This probably means taht they are somewhat related.

##Exercise 10

score = 3.98 + .068(beauty) + -.16(tenure track) + -.13(tenured)

This means that for someone who is just teaching, one unit changes in beauty scoers increase evaluations scores by .068. For someone who is tenured, beatuy has the same effect (+.068) they have a lower baseline comapared to professors who are teaching (-.16). This is the same for tenured professors (-.13). 

```{r rank}
m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
summary(m_bty_rank)
```
##Exercise 11
I think cls_profs will be the worst predictor of evaluation scores from that group. My thinking is that whether it is a one or many professors teaching that same course will not affect a single professors evaluations.

## Exercise 12

Yeah the R2 seems pretty low.

```{r cls_profs}
m_clsprofs <- lm(score ~cls_profs, data = evals)
summary(m_clsprofs)
```

##Exercise 13
If i am including cls_perc_eval and cls_students in the model then i should not also include cls_did_eval because that is mathematically the same as the first two which would reduce the adjusted R2 because it does not add any additional predictive ability.

##Exercise 14
```{r all}
m_all <- lm(score ~ rank + ethnicity + gender + language + age + 
             cls_perc_eval + cls_students + cls_level + cls_profs + 
             cls_credits + bty_avg, data = evals)
summary(m_all)
```

##Exercise 15
backward

score = 3.51 +.208(ethnicity_notminority) + .15(gender_male) + .58(class credit) + .08(beauty)

```{r 2}
m_4 <- lm(score ~  ethnicity + gender  + 
             cls_credits + bty_avg, data = evals)
summary(m_4)
```

##Exercise 16
the slope of beauty is .08 which means that for every 1 unit increase in beauty scores, the evaluation score increases by .08.
The slope of gender is .15 which means that when a professor is a male (as opposed to a female) their evaluation scores are .15 points higher.

##Exercise 17
Based on this model a person with a high score is likely to be white, male, very attractive, and teach a 1 credit course.

## Exercise 18 
While i think that this finding would likely replicate at another school, i would not want to generalize too much. Especially because these results might be different at a smaller school or a school in a more diverse environment.